Innovation and elaboration on the avian tree of life - supplementary materials

### 2023-06-01 Manuscript/supplementaries.tex
Update supplementaries.tex

\begin{figure}[htpb]
\centering
   \includegraphics[width=0.5\textwidth]{Figures/random_skewers.pdf}
\caption{Random skewers test for the differences between the super orders (in purple) and the orders (in gold) variance-covariance matrices against the whole phylogeny ones. And, in light gold, between the orders and their super-orders variance covariance matrices. The different line types (dashed and full) represent respectively the 95\% and the 75\% CI distribution and the dots represent the median skewer correlation estimate. The stars denote the median p-value estimate (0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1).}
\label{Fig:random_skewers}
\end{figure}

@@

\begin{figure}[!htbp]
\centering
    \includegraphics[width=0.9\textwidth]{Figures/InnovElabTree_passerine_supplement.pdf}
\caption{Passeriformes phylogeny coloured by beak shape innovation and elaboration level. See the caption of figure 1 in the main text for details.}
\label{fig_phylogeny_passeriformes}
\end{figure}

>>>>

\begin{figure}[htpb]
\centering
   \includegraphics[width=0.5\textwidth]{Figures/random_skewers.pdf}
\caption{Random skewers test for the differences between the super orders (in purple) and the orders (in gold) variance-covariance matrices against the whole phylogeny ones. And, in light gold, between the orders and their super-orders variance covariance matrices. The different line types (dashed and full) represent respectively the 95\% and the 75\% CI distribution and the dots represent the median skewer correlation estimate. The stars denote the median p-value estimate (0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1).}
\label{/home/tguillerme/Projects/elaboration_exploration_bird_beaks/Manuscript/Figures/others/figure_phylo_spiro_dark.png
/home/tguillerme/Projects/elaboration_exploration_bird_beaks/Manuscript/Figures/others/orthogonality_results.png
/home/tguillerme/Projects/elaboration_exploration_bird_beaks/Manuscript/Figures/others/relative_EI_gg_style.png}
\end{figure}

@@

\begin{figure}[!htbp]
\centering
    \includegraphics[width=0.9\textwidth]{Figures/InnovElabTree_passerine_supplement_revised.pdf}
\caption{Passeriformes phylogeny coloured by beak shape innovation and elaboration level. See the caption of figure 2 in the main text for details.}
\label{fig_phylogeny_passeriformes}
\end{figure}
